%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[12pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{tgpagella}
\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
% adjust the page margins
\usepackage[scale=0.845]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Haopeng (Hoppe)}{Wang}                               % optional, remove / comment the line if not wanted
\address{Burnaby, BC, CA}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{236-862-2640}                   % optional, remove / comment the line if not wanted            % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{hwa125@sfu.ca}                               % optional, remove / comment the line if not wanted
\homepage{github.com/wanghoppe}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%]\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
% \small{Undergraduate electrical and electronic engineer completing the final year of a master's degree. Passionate about science, with strong technical, business, and interpersonal skills for working in a team and successfully completing a project.}
\section{Summary of Skills}

\vspace{3pt}

\subsection{Technical Skills}

\vspace{3pt}

\begin{itemize}

\item{\textbf{Programming Language}: Python, SQL, Javascript, Java, HTML, C++, C, Matlab, R.}
\vspace{2pt}
\item{\textbf{Big Data/ Data Science techniques}: Hadoop, Spark, Cassandra, Kubernetes, Pandas, Jupyter}
\vspace{2pt}
\item{\textbf{Machine Leaning/ Deep Learning}:Tensorflow, Tensorlayer, Keras, Pytorch, Scikit-Learn.}
\vspace{2pt}
\item{\textbf{Tools/ Framework}: AWS, Git, React (Native), Expo, Node.js, Django, Android Studio, RabbitMQ}
\end{itemize}

\vspace{8pt}

\subsection{Transferrable Skills}

\vspace{3pt}

\begin{itemize}

\item{\textbf{Active and quick learner }{for knowledge and new techs: self-learned many techs/framework as well as online MOOCs and applied the knowledge learned to self-directed projects.}}
\vspace{3pt}

\item{\textbf{Good collaboration abilities }{obtained from previous Co-op experience and working with project team members by solving conflicts and helping others in need.}}


\end{itemize}

\vspace{8pt}

\section{Work Experience}

\begin{itemize}
\vspace{6pt}

\item{\cventry{May 2019 - Dec 2019}{Software Engineer, Data Aggregation Co-op}{Realtor.com}{Richmond, BC, Canada}{}{}

\begin{itemize}
\item{Worked collaboratively in an Agile/Scrum team to maintain our listing data pipeline and create real estate specific data transformation rule with Java and Javascript.}
\vspace{3pt}
\item{Responsible for resolving customer's and downstream's data-related issues, including data accuracy, data richness, and pipeline performance.
}
\vspace{3pt}
\item{Helped our team migrate special datasources to the new data pipeline by writing python scripts to provide migration metrics and automation.}
\vspace{3pt}
\item{Linked Mysql database to Google Sheet using AWS Lambda and Google Sheet API to create a daily auto-generated report which is used to monitor the status of all datasources.}

\end{itemize}}
\end{itemize}


\vspace{8pt}

\section{Selected Projects}

\vspace{6pt}

\begin{itemize}

\item{\cventry{Sept 2019 - Jan 2020}{Self-directed}{Mobile Music App Development}{}{}{}

\begin{itemize}
\item{Built a mobile application which allows users to extract Youtube audio to the cloud (AWS S3), and provided the functionalities to steam, download, play, and manage the audio within the application.}
\vspace{3pt}
\item{Powered by React Native, and can be built to run on both iOS and Android devices.}
\vspace{3pt}
\item{Deployed the back end service with AWS Lambda and API Gateway and go completely serverless with high scalability and simplicity.}
\end{itemize}}

\vspace{14pt}

\item{\cventry{Apr 2019}{Programming for Big Data II Course Project}{Cryptocurrency Real-Time Prediction System}{Simon Fraser University}{}{}

\begin{itemize}
\item{Developed a deep learning model (LSTM RNN) to predict Bitcoin price by integrating historical and social media data with news sentiment analysis.}
\vspace{3pt}
\item{Built a streaming system, which includes pipelines for data collection and feature extraction, model prediction, RabbitMQ result publishing, and Node.js Server-Sent Events (SSE), to send real-time price prediction to our web front end.}
\vspace{3pt}
\item{Our \textcolor{cyan}{\href{http://crypto-host.s3-website-us-west-2.amazonaws.com}{React web front end}} is capable updating charts itself with new incoming prediction as well as displaying the latest cryptocurrency market information and some statistical analysis.}
\end{itemize}}

\vspace{14pt}

\item{\cventry{Dec 2018}{Machine Learning Course Project}{Low Resolution Dark Image Enhancement}{Simon Fraser University}{}{}

\begin{itemize}
\item{Based on the Learning-to-See-in-Dark model, and combined it with SRGAN (Super Resolution GAN) to achieve 4x super-resolution as well as denoising, deblurring, and white balance adjustment for low resolution low light image.}
\vspace{3pt}
\item{Used the dataset provided by the Learning-to-See-in-Dark model, and built our own training data preparation pipeline, which includes image resizing, cropping, and data augmentation.}
\vspace{3pt}
\item{Solved the limitation of original See-in-Dark model: which needs raw HD image data as input.}

\end{itemize}}

\vspace{14pt}

\item{\cventry{Jun 2018}{Graduation Project}{Rhythm Reconstruction Using RNN}{Xi'an Jiaotong University}{}{}

\begin{itemize}
\item{Built a 3-layer LSTM RNN to learn the rhythmic structure of modern music: reconstructing the pitches from existing music pieces to form new melodies, which can have a style similar to the original one or being totally different.}
\vspace{3pt}
\item{Based on Google Brain Magenta project, used Tensorflow to build and train the model.}
\vspace{3pt}
\item{Applied some techniques includes data augmentation, attention mechanism, and drop off to achieve better performance.}
\end{itemize}}

\end{itemize}
\vspace{8pt}

\section{Education}

\vspace{6pt}

\begin{itemize}


\item{\cventry{Sept 2018 - Present}{MSc in Computer Science (Big Data) }{Simon Fraser University}{Burnaby, BC, Canada}{}{GPA: 3.78/ 4.33}}
\vspace{3pt}

\item{\cventry{Sept 2014 - Jun 2018}{Bachelor of Energy and Power Engineering}{Xi’an Jiaotong University}{Xi’an, China}{}{GPA: 84/ 100}}

\end{itemize}
\vspace{8pt}
\section{MOOC Certificates}

\vspace{6pt}

\begin{itemize}

\item{\textbf{From Stanford Online:}
\vspace{3pt}
\begin{itemize}
\item{Algorithms: Design and Analysis, \textit{Stanford University}\hfill{grade:  93\%}}
\vspace{3pt}
\end{itemize}}


\item{\textbf{From Coursera:}
\vspace{3pt}
\begin{itemize}
\item{Neural Networks and Deep Learning, \textit{deeplearning.ai}\hfill{grade:  92\%}}
\vspace{3pt}

\item{Machine Learning, \textit{Stanford University}\hfill{grade:  96\%}}
\vspace{3pt}

\end{itemize}}

\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
